Forecasting the 2024 U.S. Presidential Election Results: Linear Regression, Bayesian and Spline-Fit Gaussian Model by Using Pollsters' Data From Five Thirty Eight

### 2024-11-04 paper/paper.qmd
minor error fixed

library(tidyverse)
library(rstanarm)
library(splines)
library(broom)
library(knitr)
library(stringr)
library(patchwork)
```

@@

The remainder of this paper is structured as follows. @sec-data discusses the data used for this analysis, including key variables and sources, with particular attention to the quality metrics that affect polling accuracy. @sec-models outlines our modeling approach for each candidate, incorporating lessons learned from recent electoral cycles. @sec-predict presents our *** predictions based on the model outputs. @sec-discuss discusses the implications of our findings and suggests directions for future research. Finally, @sec-appendix evaluates Trafalgar Group’s polling methodology, and our idealized methodology and survey copy.

This paper examines the development of a multiple linear regression (MLR) model to predict the percentage of support (pct) for U.S. presidential candidates based on polling data. The data includes a range of predictors, such as sample size, pollster quality factors, and time-related factors. The focus of the analysis is on nationwide polling data, aggregated from different pollsters, to create a robust model for forecasting election outcomes. The goal is to provide a clearer understanding of how various poll attributes influence polling results and to derive insights that can predict election outcomes.

Our Results shows that

This analysis is useful in understanding how various polling factors contribute to predicting election results. By modeling the relationship between polling result and factors, the study enhances the ability to forecast election outcomes based on public opinion data. This model provides a practical tool for researchers, political strategists, and analysts to assess the reliability of polling data and its implications for elections.

This paper develops statistical models to forecast the 2024 presidential election outcome between Kamala Harris and Donald Trump. Utilizing multiple linear regression, we predict the support percentages for each candidate across various states, incorporating essential factors such as pollster rating, sample size, and state-specific demographics. By aggregating these state-level predictions, we simulate possible outcomes to estimate each candidate's probability of achieving the necessary 270 electoral votes. Additionally, we analyze [@trafalgar_polling_methodology] polling methodology and propose an optimized survey and methodology aimed at improving election forecast accuracy.

The remainder of this paper is structured as follows. @sec-data discusses the data used for this analysis, including key variables and sources, with particular attention to the quality metrics that affect polling accuracy. @sec-models outlines our modeling approach for each candidate, incorporating lessons learned from recent electoral cycles. @sec-predict presents our *** predictions based on the model outputs. @sec-discuss discusses the implications of our findings and suggests directions for future research. Finally, @sec-appendix evaluates Trafalgar Group’s polling methodology, and our idealized methodology and survey copy.

@@

five_rows <- as_tibble(cleaned_data)
five_rows <- five_rows %>%
  rename_with(~ str_replace_all(., "_", " "))
five_rows %>% 
  slice(1:5)

>>>>

library(tidyverse)
library(rstanarm)
library(splines)
library(broom)
library(knitr)
library(stringr)
library(patchwork)
library(kableExtra)
```

@@

The remainder of this paper is structured as follows. @sec-data discusses the data used for this analysis, including key variables and sources, with particular attention to the quality metrics that affect polling accuracy. @sec-models outlines our modeling approach for each candidate, incorporating lessons learned from recent electoral cycles. Results of each model are discussed under the specific model section @sec-discuss discusses the implications of our findings and suggests directions for future research. Finally, @sec-appendix evaluates Trafalgar Group’s polling methodology, and our idealized methodology and survey copy.

@@

cleaned_data_subset <- head(cleaned_data, 5)
colnames(cleaned_data_subset) <- c("pollster"	, "sample size", "poll grade", 
                                   "pollscore","state", "transparency score", 
                                   "poll end date", "party", "candidate", 
                                   "percentage")
kable(cleaned_data_subset, digits = 2) %>%
    kable_styling(font_size = 6) 
```
